Proof nets for first-order additive linear logic

### 2018-01-17 ALL1.tex
stuff

\newcommand\seq[3][]{{\vdash_{#1}}#2,#3}
\newcommand\fv{\textsc{fv}}

@@

\newcommand\init[2]{#1\star #2}

@@

\newcommand\qrr[1]{
  \ifx#1+\expandafter\@qrr\else
  \ifx#1*\*\mathrm R\else
  \ifx#1!\forall\mathrm R\else
  \ifx#1?\expandafter\@@qrr\else
  \ifx#11\mathrm{ax}\else
  #1\mathrm R
  \fi\fi\fi\fi\fi
}
\newcommand\@qrr[1]{+\mathrm R,#1}
\newcommand\@@qrr[1]{\exists\mathrm R,#1}

@@

\newcommand\urr[1]{
  \ifx#1+\expandafter\@urr\else
  \ifx#1*\*\mathrm U\else
  \ifx#1!\forall\mathrm U\else
  \ifx#1?\exists\mathrm U\else 
  \ifx#11\mathrm{axU}\else
  #1\mathrm U
  \fi\fi\fi\fi\fi
}
\newcommand\@urr[1]{+_{#1}\mathrm U}

@@

@@

@@

First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
%
\setMidspace{5pt}
\[
\begin{array}{@{}l@{}l}
	t &\Coloneqq x \Mid f(t_1,\dots,t_n)
\\[10pt]
	a &\Coloneqq P(t_1,\dots,t_n) \Mid \dual P(t_1,\dots,t_n)
\\[10pt]
	A &\Coloneqq a \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall x.A
\end{array}
\]
%
Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$, as a matter of convenience. The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan. We use the following notational conventions.
%
\[
\begin{tabular}{@{}lll@{}} 
	$x,y,z$ & $\in \var$		& first-order variables\\
	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
	$P,Q,R$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
	$s,t,u$ & $\in \terms$ 		& first-order terms over $\var$ and $\Sigma_f$ \\
	$a,b,c$ & $\in \atom$		& atomic propositions \\
	$A,B,C$ & $\in \form$		& \all1 formulas \\
\end{tabular}
\]
%
A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$. A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent. We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$.

@@

A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to\var\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map. We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.
% When a link is not a witness link, this may be emphasized by calling it \defn{clean}.

@@

	\item[Freshness]
For a link $\link CD$ over $\seq AB$, variables in the range of $\sigma$ are \emph{fresh}: distinct from any existentially quantified variable in $\seq AB$.

	\item[Eigenvariables not free]
For a link $\link CD$ over $\seq AB$, if a variable $x$ in the range of $\sigma$ is universally quantified as $\forall x.X$ in $\seq AB$ (an \emph{eigenvariable}), then $C\leq X$ or $D\leq X$.
\end{description}

\begin{definition}
The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows.
%
% $\net{\lambda_\Sigma}AB$ where $\lambda_\Sigma=\deseq[\varnothing]\pi AB$ and the function $\deseq-AB$ is defined as follows.
%
%\newlength\deseqwidth
%\settowidth\deseqwidth{$\scriptstyle{A'\,,\,B'_0\+B'_1}$}
%
\newcommand\XDeseq[4][\sigma]{
 \left[\vcenter{#2}\right]%
 _{\makebox[0pt][l]{$\scriptstyle{#1}$}}%
 ^{\makebox[0pt][l]{$\scriptstyle{#3\,,\,#4}$}}%
 \rule{35pt}{0pt}
}
%
\begin{align*}
	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{}}bc &\quad=\quad \{\link bc\}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr+i]{\seq A {B_1\+B_2}}{\Prf \pi A{B_i}}} {A'} {B_1'\+B'_2} 
	& \quad=\quad 
	\Deseq{\Prf\pi A{B_i}} {A'} {B_i'}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr*]{\seq A{B\*C}}{
	 \Prf\pi AB && \Prf{\pi'}AC 
	}}{A'}{B'\*C'}
	& \quad=\quad 
	  \Deseq{\Prf\pi AB}{A'}{B'}
	  \cup
	  \Deseq{\Prf{\pi'}AC}{A'}{C'}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr?t]{\seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}}{A'}{\exists x.B'}
	& \quad=\quad 
	 \Deseq[{\sigma[t/x]}]{\Prf\pi A{B[t/x]}} {A'} {B'}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr!]
	  {\seq A{\forall x.B}}{\Prf\pi AB}} {A'} {\forall x.B'}
	& \quad=\quad 
	  \Deseq{\Prf\pi AB}{A'}{B'}
\end{align*}
\end{definition}

@@

\begin{definition}
A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
\[
	\dom\sigma = \ex[A]C\cup\ex[B]D~.
\]
\end{definition}
%
The witness map $\sigma$ of a link $\link CD$ then has two natural components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.

@@

%\begin{figure}
%\[
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
%    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{1,1}
%    \end{tikzpicture}}
%\scoal 
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{D*{_1}{{\+}}D*{_2}}
%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
%    \end{tikzpicture}}
%\hfill% 
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
%    	\Vlink[red,label={$\scriptstyle\sigma~$},l]{[-1]1,1}
%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{[1]1,3}
%    \end{tikzpicture}}
%\scoal
%	\vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{D*{_1}{{\*}}D*{_2}}
%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,2}
%    \end{tikzpicture}} 
%\hfill%    
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{\exists x.D}
%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
%    \end{tikzpicture}}
%\stackrel{\begin{array}{@{}c@{}}\scriptstyle x\,\in\\[-1ex]\scriptstyle\dom\sigma\end{array}}\scoal
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{\exists x.D}
%    	\Vlink[red,label={~$\scriptstyle{\sigma\minus x}$}]{1,1}
%    \end{tikzpicture}}   
%\hfill%
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{\forall x.D}
%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,4}
%    \end{tikzpicture}}
%\stackrel{x\,\notin\,\sigma}\scoal
%    \vc{\begin{tikzpicture}[net]
%    	\formula[y=2]{C}
%    	\formula[y=1]{\forall x.D}
%    	\Vlink[red,label={~$\scriptstyle\sigma$}]{1,1}
%    \end{tikzpicture}}
%\]
%\caption{Coalescence rules}
%\label{fig:coalescence}
%\end{figure}

@@

\begin{definition}
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
%
\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, that replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ (where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively).
%
\begin{align*}
%\tag{$\srr+i$}
	\link C{D_i}^\pi
	& \scoal
	\link C{D_1\+D_2}^\psi
	&& 
 	\psi=~\vc{\infer[\Qrr+i]{\seq{C\sigma}{D_1\sigma\,\+\,D_2\sigma}}  {\Prf \pi {C\sigma} {D_i\sigma}}}
\\ \\[-8pt]
%\tag{$\srr*$}
	%\{\link C{D_1}^\pi\,,\,\link C{D_2}^\phi\}
	\left.\begin{array}{@{}l@{\,}}\link C{D_1}^\pi \\ \link C{D_2}^\phi\end{array}\right\}
	& \scoal
	\link C{D_1\*D_2}^\psi
	&&
	\psi=~\vc{\infer[\Qrr*]{\seq{C\sigma}{D_1\sigma\,\*\,D_2\sigma}}  {
      \Prf \pi {C\sigma} {D_1\sigma} & \Prf \phi {C\sigma} {D_2\sigma}    
	}}
\\ \\[-8pt]
%\tag{$\srr?$}
	\link CD^\pi
	& \scoal
	\link[\sigma\minus x]C{\exists x.D}^\psi
	\quad{\scriptstyle(x\,\in\,\dom\sigma)}
	&&
	\psi=~\vc{\infer[\Qrr?{\sigma(x)}]{\seq{C(\sigma\minus x)}{\exists x.D(\sigma\minus x)}} {\Prf \pi {C\sigma} {D\sigma} }}	
\\ \\[-8pt]
%\tag{$\srr!$}
	\link CD^\pi
	& \scoal
	\link C{\forall x.D}^\psi
	\quad{\scriptstyle\phantom{\minus x}(x\,\notin\,\sigma)}
	&&
	\psi=~\vc{\infer[\Qrr!]{\seq{C\sigma}{\forall x.D\sigma}} {\Prf \pi {C\sigma} {D\sigma}}}
\end{align*}
%
\defn{Strict coalescence} is the same relation on witness pre-nets, ignoring proof labels, illustrated in Figure~\ref{fig:coalescence}. A witness pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces to $\net{\{\link[\varnothing]AB\}}AB$. It \defn{strongly} strict-coalesces if any coalescence path terminates at $\net{\{\link[\varnothing]AB\}}AB$.
\end{definition}

@@

\begin{theorem}
For any \all1 proof $\pi$, the de-sequentialization $[\pi]$ is a witness net that sequentializes to $\pi$. 
\end{theorem}

@@

@@

%It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
%
\begin{definition}
A witness pre-net is \defn{correct} if
\begin{itemize}
\item it has exact coverage,
\item it is \defn{slice-correct}: every slice is a singleton, and
\item it is \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
\end{itemize}
\end{definition}

@@

@@

\begin{proposition}
If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
\[
	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
	 \Prf\pi AB & \Prf\phi{\dual B}C
	}
\]
\end{proposition}

>>>>

\newcommand\seq[2]{{\vdash}#1,#2}
\newcommand\fv{\textsc{fv}}

@@

\newcommand\init[2]{\mgu(#1,#2)}

@@

\newcommand\qrr[1]{
  \ifx#1+\expandafter\@qrr\else
  \ifx#1*\*\mathrm R\else
  \ifx#1!\forall\mathrm R\else
  \ifx#1?\expandafter\@@qrr\else
  \ifx#11\mathrm{ax}\else
  \ifx#1.\mathrm{cut}\else
  #1\mathrm R
  \fi\fi\fi\fi\fi\fi
}
\newcommand\@qrr[1]{+\mathrm R,#1}
\newcommand\@@qrr[1]{\exists\mathrm R,#1}

@@

\newcommand\urr[1]{
  \ifx#1+\expandafter\@urr\else
  \ifx#1*\*\mathrm U\else
  \ifx#1!\forall\mathrm U\else
  \ifx#1?\exists\mathrm U\else 
  \ifx#11\mathrm{axU}\else
  #1\mathrm U
  \fi\fi\fi\fi\fi
}
\newcommand\@urr[1]{+\mathrm U,{#1}}

@@

% ===== Permutations

\newcommand\downperm{\sim\rule[-8pt]{0pt}{22pt}}

\newcommand\permAB{
 \infer[\Qrr!]{\Seq{\forall x.A}{\forall y.B}}{
  \infer[\Qrr!]{\Seq A{\forall y.B}}{
   \Seq AB
}}}
\newcommand\permBA{
 \infer[\Qrr!]{\Seq{\forall x.A}{\forall y.B}}{
  \infer[\Qrr!]{\Seq{\forall x.A}B}{
   \Seq AB
}}}
\newcommand\permAE{
 \infer[\Qrr!]{\Seq{\forall x.A}{\exists y.B}}{
  \infer[\Qrr?t]{\Seq A{\exists y.B}}{
   \Seq A{B[t/y]}
}}}
\newcommand\permEA{
 \infer[\Qrr?t]{\Seq{\forall x.A}{\forall y.B}}{
  \infer[\Qrr!]{\Seq{\forall x.A}{B[t/y]}}{
   \Seq A{B[t/y]}
}}}
\newcommand\permEF{
 \infer[\Qrr?s]{\Seq{\exists x.A}{\exists y.B}}{
  \infer[\Qrr?t]{\Seq{A[s/x]}{\exists y.B}}{
   \Seq{A[s/x]}{B[t/y]}
}}}
\newcommand\permFE{
 \infer[\Qrr?t]{\Seq{\exists x.A}{\exists y.B}}{
  \infer[\Qrr?s]{\Seq{\exists x.A}B[t/y]}{
   \Seq{A[s/x]}{B[t/y]}
}}}
\newcommand\permAP{
 \infer[\Qrr!]{\Seq{\forall x.A}{B_1\+B_2}}{
  \infer[\Qrr+i]{\Seq A{B_1\+B_2}}{
   \Seq A{B_i}
}}}
\newcommand\permPA{
 \infer[\Qrr+i]{\Seq{\forall x.A}{B_1\+B_2}}{
  \infer[\Qrr!]{\Seq{\forall x.A}{B_i}}{
   \Seq A{B_i}
}}}
\newcommand\permEP{
 \infer[\Qrr?t]{\Seq{\exists x.A}{B_1\+B_2}}{
  \infer[\Qrr+i]{\Seq{A[t/x]}{B_1\+B_2}}{
   \Seq{A[t/x]}{B_i}
}}}
\newcommand\permPE{
 \infer[\Qrr+i]{\Seq{\exists x.A}{B_1\+B_2}}{
  \infer[\Qrr?t]{\Seq{\exists x.A}{B_i}}{
   \Seq{A[t/x]}{B_i}
}}}
\newcommand\permPQ{
 \infer[\Qrr+i]{\Seq{A_1\+A_2}{B_1\+B_2}}{
  \infer[\Qrr+j]{\Seq{A_i}{B_1\+B_2}}{
   \Seq{A_i}{B_j}
}}}
\newcommand\permQP{
 \infer[\Qrr+j]{\Seq{A_1\+A_2}{B_1\+B_2}}{
  \infer[\Qrr+i]{\Seq{A_1\+A_2}{B_j}}{
   \Seq{A_i}{B_j}
}}}
\newcommand\permAX{
 \infer[\Qrr!]{\Seq{\forall x.A}{B\*C}}{
  \infer[\Qrr*]{\Seq A{B\*C}}{
   \Seq AB & \Seq AC
}}}
\newcommand\permXA{
 \infer[\Qrr*]{\Seq{\forall x.A}{B\*C}}{
  \infer[\Qrr!]{\Seq{\forall x.A}B}{
   \Seq AB 
  }& 
  \infer[\Qrr!]{\Seq{\forall x.A}C}{
   \Seq AC
}}}
\newcommand\permEX{
 \infer[\Qrr?t]{\Seq{\exists x.A}{B\*C}}{
  \infer[\Qrr*]{\Seq{A[t/x]}{B\*C}}{
   \Seq{A[t/x]}B & \Seq{A[t/x]}C
}}}
\newcommand\permXE{
 \infer[\Qrr*]{\Seq{\exists x.A}{B\*C}}{
  \infer[\Qrr?t]{\Seq{\exists x.A}B}{
   \Seq{A[t/x]}B 
  }& 
  \infer[\Qrr?t]{\Seq{\exists x.A}C}{
   \Seq{A[t/x]}C
}}}
\newcommand\permPX{
 \infer[\Qrr+i]{\Seq{A_1\+A_2}{B\*C}}{
  \infer[\Qrr*]{\Seq{A_i}{B\*C}}{
   \Seq{A_i}B & \Seq{A_i}C
}}}
\newcommand\permXP{
 \infer[\Qrr*]{\Seq{A_1\+A_2}{B\*C}}{
  \infer[\Qrr+i]{\Seq{A_1\+A_2}B}{
   \Seq{A_i}B 
  }& 
  \infer[\Qrr+i]{\Seq{A_1\+A_2}C}{
   \Seq{A_i}C
}}}
\newcommand\permXY{
 \infer[\Qrr*]{\Seq{A\*B}{C\*D}}{
  \infer[\Qrr*]{\Seq A{C\*D}}{
   \Seq AC & \Seq AD
  }&
  \infer[\Qrr*]{\Seq B{C\*D}}{
   \Seq BC & \Seq BD
}}}
\newcommand\permYX{
 \infer[\Qrr*]{\Seq{A\*B}{C\*D}}{
  \infer[\Qrr*]{\Seq{A\*B}C}{
   \Seq AC & \Seq BC
  }&
  \infer[\Qrr*]{\Seq{A\*B}D}{
   \Seq AD & \Seq BD
}}}

% ===== Cut-permutations

\newcommand\permAC{
 \infer[\Qrr.]{\Seq{\forall x.A}C}{
  \infer[\Qrr!]{\Seq{\forall x.A}B}{
   \Seq AB 
  }& 
  \Seq{\dual B}C
}}
\newcommand\permCA{
 \infer[\Qrr!]{\Seq{\forall x.A}C}{
  \infer[\Qrr.]{\Seq AC}{
   \Seq AB & \Seq{\dual B}C
}}}
\newcommand\permEC{
 \infer[\Qrr.]{\Seq{\exists x.A}C}{
  \infer[\Qrr?t]{\Seq{\exists x.A}B}{
   \Seq{A[t/x]}B 
  }& 
  \Seq{\dual B}C
}}
\newcommand\permCE{
 \infer[\Qrr?t]{\Seq{\exists x.A}C}{
  \infer[\Qrr.]{\Seq{A[t/x]}C}{
   \Seq{A[t/x]}B & \Seq{\dual B}C
}}}
\newcommand\permPC{
 \infer[\Qrr.]{\Seq{{A_1\+A_2}}C}{
  \infer[\Qrr+i]{\Seq{{A_1\+A_2}}B}{
   \Seq {A_i}B 
  }& 
  \Seq{\dual B}C
}}
\newcommand\permCP{
 \infer[\Qrr+i]{\Seq{{A_1\+A_2}}C}{
  \infer[\Qrr.]{\Seq {A_i}C}{
   \Seq {A_i}B & \Seq{\dual B}C
}}}
\newcommand\permXC{
 \infer[\Qrr.]{\Seq{{A_1\*A_2}}C}{
  \infer[\Qrr*]{\Seq{{A_1\*A_2}}B}{
   \Seq {A_1}B & \Seq{A_2}B
  }& 
  \Seq{\dual B}C
}}
\newcommand\permCX{
 \infer[\Qrr*]{\Seq{{A_1\*A_2}}C}{
  \infer[\Qrr.]{\Seq {A_i}C}{
   \Seq {A_1}B & \Seq{\dual B}C
  }&
  \infer[\Qrr.]{\Seq {A_i}C}{
   \Seq {A_2}B & \Seq{\dual B}C
}}}
\newcommand\permCD{
 \infer[\Qrr.]{\Seq AD}{
  \infer[\Qrr.]{\Seq AC}{
   \Seq AB & \Seq{\dual B}C
  }& 
  \Seq{\dual C}D
}}
\newcommand\permDC{
 \infer[\Qrr.]{\Seq{{A_1\*A_2}}C}{
  \Seq A{\dual B}
  &
  \infer[\Qrr.]{\Seq BD}{
   \Seq B{\dual C} & \Seq CD
}}}

@@

\begin{lemma}
For $\link ab$ in a proof net $\net{\lambda_\star}AB$ and $\link[\tau]{\dual b}c$ in $\net{\kappa_\star}{\dual B}C$ the composition $\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}=\mgu(a,c)$.
\end{lemma}

\begin{proof}
Let $\rho=\mgu(a,c)$ and $\rho'=\sigma_a\tau_c\dcom\fix{\sigma_b\tau\subdual b}$. Define the \defn{basis} $\floor{s,t}$ of the $\mgu$ of $s$ and $t$ to be the substitution map defined by $\floor{x,t}=\floor{t,x} = [t/x]$ and
\[
	\floor{P(s_1,\dots,s_n),P(t_1,\dots,t_n)} =
	\floor{f(s_1,\dots,s_n),f(t_1,\dots,t_n)} =
	\floor{s_1,t_1}\dots\floor{s_n,t_n}~.
\]
Write $\floor\sigma$ for the basis $\floor{a,b}$ of $\sigma$, $\floor\tau$ for that of $\tau$, and $\floor\rho$ for that of $\rho$.
\end{proof}

@@

First-order terms and the formulas of first-order $\all$ are generated by the following grammars.
%
\setMidspace{5pt}
\[
\begin{array}{@{}l@{}l}
	t &\Coloneqq x \Mid f(t_1,\dots,t_n)
\\[10pt]
	a &\Coloneqq P(t_1,\dots,t_n) \Mid \dual P(t_1,\dots,t_n)
\\[10pt]
	A &\Coloneqq a \Mid A\+A \Mid A\*A \Mid \exists x.A \Mid \forall x.A
\end{array}
\]
%
Negation $(\dual{\,\cdot\,})$ is applied to predicate symbols, $\dual P$, as a matter of convenience. The \defn{dual} $\dual A$ of an arbitrary formula $A$ is given by DeMorgan. We use the following notational conventions.
%
\[
\begin{tabular}{@{}lll@{}} 
	$x,y,z$ & $\in \var$		& first-order variables\\
	$f,g,h$ & $\in \Sigma_f$	& $n$-ary $(n\geq 0)$ function symbols from a fixed alphabet $\Sigma_f$\\
	$P,Q,R$ & $\in \Sigma_p$	& $n$-ary $(n\geq 0)$ predicate symbols from a fixed alphabet $\Sigma_p$ \\
	$s,t,u$ & $\in \terms$ 		& first-order terms over $\var$ and $\Sigma_f$ \\
	$a,b,c$ & $\in \atom$		& atomic propositions \\
	$A,B,C$ & $\in \form$		& \all1 formulas \\
\end{tabular}
\]
%
A \defn{sequent} $\seq AB$ is a pair of formulas $A$ and $B$. A sequent calculus for \all1 is given in Figure~\ref{fig:sequent calculus}, where each rule has a symmetric counterpart that applies to the first formula in the sequent. We write $\prf\pi AB$ for a proof $\pi$ with conclusion sequent $\seq AB$. Two proofs are \defn{equivalent} $\pi\sim\pi'$ if one is obtained from the other by rule permutations (Appendix, Figure~\ref{fig:permutations}.

@@

A \defn{witness linking} $\lambda_\Sigma$ is a linking $\lambda$ with a \defn{witness labelling} $\Sigma\colon\lambda\to\var\rightharpoonup\terms$ that assigns each link $(C,D)$ a witness map. We may use and define $\lambda_\Sigma$ as a set of \defn{witness links} $\link CD$, where $(C,D)\in\lambda$ and $\Sigma(C,D)=\sigma$.

@@

	\item[Eigenvariables not free]
For a link $\link CD$ over $\seq AB$, if a variable $x$ in the range of $\sigma$ is universally quantified as $\forall x.X$ in $\seq AB$ (an \emph{eigenvariable}), then $C\leq X$ or $D\leq X$.

	\item[Freshness]
For a link $\link CD$ over $\seq AB$, other variables in the range of $\sigma$ are \emph{fresh}: distinct from any existentially quantified variable in $\seq AB$.
\end{description}

\begin{definition}
The \defn{de-sequentialization} $[\pi]$ of a sequent proof $\prf\pi AB$ is the witness pre-net $\net{\deseq[\varnothing]\pi AB}AB$ where the function $\deseq-AB$ is defined inductively as follows.
%
\newcommand\XDeseq[4][\sigma]{
 \left[\vcenter{#2}\right]%
 _{\makebox[0pt][l]{$\scriptstyle{#1}$}}%
 ^{\makebox[0pt][l]{$\scriptstyle{#3\,,\,#4}$}}%
 \rule{35pt}{0pt}
}
%
\begin{align*}
	\XDeseq{\,\infer[\Qrr1]{\seq a{\dual a}}{}}bc &\quad=\quad \{\link bc\}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr+i]{\seq A {B_1\+B_2}}{\Prf \pi A{B_i}}} {A'} {B_1'\+B'_2} 
	& \quad=\quad 
	\Deseq{\Prf\pi A{B_i}} {A'} {B_i'}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr*]{\seq A{B\*C}}{
	 \Prf\pi AB && \Prf{\pi'}AC 
	}}{A'}{B'\*C'}
	& \quad=\quad 
	  \Deseq{\Prf\pi AB}{A'}{B'}
	  \cup
	  \Deseq{\Prf{\pi'}AC}{A'}{C'}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr?t]{\seq A{\exists x.B}}{\Prf\pi A{B[t/x]}}}{A'}{\exists x.B'}
	& \quad=\quad 
	 \Deseq[{\sigma[t/x]}]{\Prf\pi A{B[t/x]}} {A'} {B'}
\\ \\[-5pt]
	\XDeseq{\infer[\Qrr!]
	  {\seq A{\forall x.B}}{\Prf\pi AB}} {A'} {\forall x.B'}
	& \quad=\quad 
	  \Deseq{\Prf\pi AB}{A'}{B'}
\end{align*}
\end{definition}

@@

\begin{definition}
A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
\[
	\dom\sigma = \ex[A]C\cup\ex[B]D~.
\]
\end{definition}
%
% ..................................................
%
The witness map $\sigma$ of a link $\link CD$ then has two natural components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.

@@

@@

\begin{definition}
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
%
\defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, that replace one or two links by another in a pre-net $\net{\lambda_\Sigma^\Pi}AB$ (where $B$ has a subformula $D_1\+D_2$, $D_1\*D_2$, $\exists x.D$, and $\forall x.D$ respectively).
%
\begin{align*}
\tag{$\srr+i$}
	\link C{D_i}^\pi
	& \scoal
	\link C{D_1\+D_2}^\psi
	&& 
 	\psi=~\vc{\infer[\Qrr+i]{\seq{C\sigma}{D_1\sigma\,\+\,D_2\sigma}}  {\Prf \pi {C\sigma} {D_i\sigma}}}
\\ \\[-8pt]
\tag{$\srr*$}
	%\{\link C{D_1}^\pi\,,\,\link C{D_2}^\phi\}
	\left.\begin{array}{@{}l@{\,}}\link C{D_1}^\pi \\ \link C{D_2}^\phi\end{array}\right\}
	& \scoal
	\link C{D_1\*D_2}^\psi
	&&
	\psi=~\vc{\infer[\Qrr*]{\seq{C\sigma}{D_1\sigma\,\*\,D_2\sigma}}  {
      \Prf \pi {C\sigma} {D_1\sigma} & \Prf \phi {C\sigma} {D_2\sigma}    
	}}
\\ \\[-8pt]
\tag{$\srr?$}
	\link CD^\pi
	& \scoal
	\link[\sigma\minus x]C{\exists x.D}^\psi
	\quad{\scriptstyle(x\,\in\,\dom\sigma)}
	&&
	\psi=~\vc{\infer[\Qrr?{\sigma(x)}]{\seq{C(\sigma\minus x)}{\exists x.D(\sigma\minus x)}} {\Prf \pi {C\sigma} {D\sigma} }}	
\\ \\[-8pt]
\tag{$\srr!$}
	\link CD^\pi
	& \scoal
	\link C{\forall x.D}^\psi
	\quad{\scriptstyle\phantom{\minus x}(x\,\notin\,\sigma)}
	&&
	\psi=~\vc{\infer[\Qrr!]{\seq{C\sigma}{\forall x.D\sigma}} {\Prf \pi {C\sigma} {D\sigma}}}
\end{align*}
%
\defn{Strict coalescence} is the same relation on witness pre-nets, ignoring proof labels, illustrated in Figure~\ref{fig:coalescence}. A witness pre-net $\net{\lambda_\Sigma}AB$ \defn{strict-coalesces} if it reduces to $\net{\{\link[\varnothing]AB\}}AB$. It \defn{strongly} strict-coalesces if any coalescence path terminates at $\net{\{\link[\varnothing]AB\}}AB$.
\end{definition}

@@

\begin{theorem}
\label{thm:proof->net->proof}
For any \all1 proof $\pi$, the witness net $[\pi]$ sequentializes to $\pi$. 
\end{theorem}

@@

\begin{theorem}
\label{thm:net->proof->net}
If $\net{\lambda_\Sigma}AB$ sequentializes to $\pi$, then $[\pi]$ is $\net{\lambda_\Sigma}AB$. 
\end{theorem}

\begin{proof}
By induction on the sequentialization path 
$\net{\lambda_\Sigma^\star}AB\scoal^*\net{\{\link[\varnothing]AB^\pi\}}AB$
it follows that in every pre-net $\net{\kappa_\Theta^\Phi}AB$ on this path, $\lambda_\Sigma$ is equal to the union over the de-sequentialization of all proof labels $\phi$ in $\Phi$:
\[
	\lambda_\Sigma=\bigcup~\{\,\deseq\phi CD \mid \link CD^\phi \in \kappa_\Theta^\Phi\,\}~.
\]
The statement is then the case $\kappa_\Theta^\Phi=\{\link[\varnothing]AB^\pi\}$.
\end{proof}

@@

%It is expected that for a more involved logic that includes multiplicative connectives, a dependency condition such as the below one needs to be applied to a slice instead.
%

\begin{definition}
A witness pre-net is \defn{correct} if
\begin{itemize}
\item it has exact coverage,
\item it is \defn{slice-correct}: every slice is a singleton, and
\item it is \defn{dependency-correct}: every column is a partial order (i.e.\ is acyclic/antisymmetric).
\end{itemize}
\end{definition}

@@

\begin{theorem}
Proof nets are canonical: $[\pi]=[\phi]$ if and only if $\pi\sim\phi$.
\end{theorem}

\begin{proof}
From left to right is by inspection of the critical pairs of sequentialization ($\scoal$). From right to left is by inspection of the rule permutations in Figure~\ref{fig:permutations} in the Appendix.
\end{proof}

@@

% ..................................................
\begin{theorem}
If proof nets $\net{\lambda_\Sigma}AB$ and $\net{\kappa_\Theta}{\dual B}C$ sequentialize to $\pi$ and $\phi$ respectively, then their composition $(\net{\lambda_\Sigma}AB)\comp(\net{\kappa_\Theta}{\dual B}C)$ sequentializes to a normal form $\psi$ of the proof
\[
	\infer[\!\!\scriptstyle{\mathrm{cut}}]{\seq AC}{
	 \Prf\pi AB & \Prf\phi{\dual B}C
	}
\]
\end{theorem}
